### 2023-11-05 manuscript/manuscript.Rmd
add the standards mix to the results table

```{r assignment-results}
tar_read(assignment_results) %>%
  left_join(tar_read(assignment_matches), 
            by = c("matrix", "technique")) %>% 
  mutate(matrix = paste(matrix,technique)#,
  ) %>%
  mutate(n_assignments = glue::glue(
    '{n_assignments} ({signif(n_assignments/n_features * 100,digits = 3)}\\%)'),
    across(where(is.numeric),~prettyNum(.x,big.mark = ','))) %>%
  select(-technique) %>% 
  dplyr::rename(`\\textit{m/z} features` = n_features,
                correlations = n_correlations,
                relationships = n_relationships,
                `assigned features` = n_assignments,
                `molecular formulas (MF)` = n_MFs,
                `KEGG compound matches` = KEGG_compound_matches,
                `KEGG MF matches` = KEGG_MF_matches,
                `matched chemical standards` = matched_standards) %>% 
  tidyr::gather(Variable,Value,-matrix) %>% 
  mutate(Value = replace(Value,
                         Value == 'NA',
                       'N/A')) %>% 
  tidyr::spread(matrix,Value) %>% 
  slice(c(1,3,8,2,7,5,4,6)) %>%
  set_colnames(stringr::str_split_fixed(colnames(.),
                                        ' ',2)[,2]) %>% 
  knitr::kable(format = 'latex',
               booktabs = TRUE,
               linesep = '',
               escape = FALSE,
               align = c(
                 rep('l',1),
                 rep('r',3)
               ),
               caption = 'A summary of the molecular formula assignment results for the example sample matrices. The number of matched chemical standards is given as the number of unique molecular formulas.') %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  add_header_above(c(
    " ", 
    "\\\\textit{B. distachyon} leaf" = 2, 
    "Human urine" = 1),
    escape = FALSE)
```

>>>>

```{r assignment-results}
tar_read(assignment_results) %>%
  left_join(tar_read(assignment_matches), 
            by = c("matrix", "technique")) %>% 
  mutate(matrix = paste(matrix,technique)#,
  ) %>%
  mutate(n_assignments = glue::glue(
    '{n_assignments} ({signif(n_assignments/n_features * 100,digits = 3)}\\%)'),
    across(where(is.numeric),~prettyNum(.x,big.mark = ','))) %>%
  select(-technique) %>% 
  dplyr::rename(`\\textit{m/z} features` = n_features,
                correlations = n_correlations,
                relationships = n_relationships,
                `assigned features` = n_assignments,
                `molecular formulas (MF)` = n_MFs,
                `KEGG compound matches` = KEGG_compound_matches,
                `KEGG MF matches` = KEGG_MF_matches,
                `matched chemical standards` = matched_standards) %>% 
  tidyr::gather(Variable,Value,-matrix) %>% 
  mutate(Value = replace(Value,
                         Value == 'NA',
                         'N/A')) %>% 
  tidyr::spread(matrix,Value) %>% 
  slice(c(1,3,8,2,7,5,4,6)) %>%
  set_colnames(stringr::str_split_fixed(colnames(.),
                                        ' ',2)[,2]) %>% 
  knitr::kable(
    format = 'latex',
    booktabs = TRUE,
    linesep = '',
    escape = FALSE,
    align = c(
      rep('l',1),
      rep('r',3)
    ),
    caption = 'A summary of the molecular formula assignment results for the example sample matrices. The number of matched chemical standards is given as the number of unique molecular formulas.') %>%
  kable_styling(latex_options = "HOLD_position") %>%
  add_header_above(c(
    " ",
    "\\\\textit{B. distachyon} leaf" = 2,
    "Human urine" = 1,
    "Standards mix" = 1),
    escape = FALSE)
```
